Developing a Comprehensive Taxonomy for REST API Faults: Insights from Real-World Bug Reports

### 2024-06-05 CS563-Project/Paper/paper.tex
Changed the paper according our findings

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{tabularx}
\usepackage{tcolorbox}
\usepackage{array}

@@

\title{Do Automated Fault Localization Techniques Work For REST APIs?}

@@

\begin{abstract}

\end{abstract}

\begin{IEEEkeywords}

\end{IEEEkeywords}

\section{Introduction}
\label{sec:introduction}

    REST APIs (Representational State Transfer) have become backbone of the modern web and cloud applications. 
    They facilitate seamless interactions between client and server through stateless communication, enabling services to be scalable, reliable, and easily integrateable ~\cite{li2016} ~\cite{neumann2018}. 
    Basically, REST APIs are a set of rules and standards  defined by OpenAPI ~\cite{ed-douibi2018} used to enable communication between different software applications over the internet. They are built around the use of standard HTTP methods such as GET, POST, PUT, and DELETE to interact with resources, which are any kind of data or service that can be named on a network.
    Given their critical role, the effective identification and resolution of faults within REST APIs remain a significant challenge ~\cite{barbir2007}, prompting the need for research on how fault localization techniques work to their unique structure and functionality.

    As systems that rely on REST APIs grow in scale and complexity  ~\cite{khare2004} , minor faults can escalate into major disruptions, impacting user experience and business operations. 
    This research is motivated by the need to evaluate how well current fault localization techniques perform in the unique context of REST APIs. 
    The goal is to determine if these techniques can indeed be applied effectively to REST APIs and, if so, to explore which types of faults are more amenable to being localized. 
    This understanding could potentially allow developers to more efficiently diagnose and address issues, thereby enhancing the stability and performance of REST API-based systems.

    Fault localization is a well-established area of research within software engineering, traditionally concentrated on more conventional software systems. 
    REST APIs, however, present distinct challenges that complicate fault localization due to their composition and operational dynamics. 
    Additionally, the architecture of REST APIs often involves diverse artifacts that are not source code, such as configuration files, API specifications, and database schemas.

    The primary objective of this research is to evaluate the effectiveness of existing fault localization techniques within the unique context of REST APIs, which feature a mix of code and non-code artifacts. 
    This study will systematically apply established fault localization methods like BLUES ~\cite{ManishBluesFaultLocalization} and LLMAO ~\cite{LLMAOFaultLocalization} to a dataset of REST API faults. 
    This dataset will be meticulously developed to represent a wide range of faults typical in REST APIs and classified according to an existing comprehensive taxonomy derived from previous research.

    This approach will enable us to assess the applicability of these fault localization techniques to REST APIs by determining how effectively they can identify and localize different types of faults. 
    The analysis will provide insights into whether traditional fault localization methods are suited to the complexities of REST APIs, especially considering their unique structural and functional characteristics.

    Our assumptions:
    \begin{itemize}

        \item \textit{Assumption:} Assume that the selected fault localization techniques are suitable for application to REST APIs, despite their original design for conventional software systems. This includes the assumption that these techniques can handle the unique challenges posed by REST APIs, such as dealing with non-code artifacts.
    \end{itemize}

    The primary research questions are formulated as follows:
    \begin{itemize}
        \item \textbf{RQ1:} What categories of faults are most effectively localized by current techniques?
        \item \textbf{RQ2:} Which fault localization technique is highly effective in the context of REST APIs?
    \end{itemize}

For the evaluation dataset, we will manually select the issues from the GitHub services and their fixes from REST API projects that utilize Spring Boot or Jersey frameworks. These GitHub services are used in the paper  \textit{Generating REST API Specifications through Static Analysis} by Manish et al ~\cite{ManishRestServices}
This dataset will encompass various categories of faults identified in REST APIs. By analyzing repositories and commit histories, we will extract specific instances where bugs have been documented and subsequently fixed. 
The categorization of these faults will be categorized with an established taxonomy of API faults ~\cite{automatedTestTaxonomy} , ensuring that each bug is classified according to its nature and impact. This rigorous dataset compilation aims to provide a comprehensive basis for testing fault localization techniques within a controlled, relevant environment.

For evaluation of fault localization techniques using the dataset derived from REST APIs employing Spring Boot and Jersey frameworks will be measured by Top-k accuracy, and EXAM score.
These metrics will collectively provide a thorough assessment of each fault localization technique's ability to detect and accurately categorize faults in REST APIs, contributing to a detailed understanding of their practical utility and areas for improvement.

\section{Background and Motivation}
\label{sec:background-and-motivation}

\subsection{Importance of REST APIs}

REST APIs (Representational State Transfer APIs) are central to modern web and cloud applications, serving as critical conduits for data exchange and system integration. 
They leverage standard HTTP methods like GET, POST, PUT, and DELETE to interact with networked resources, making them integral to the architecture of distributed systems. 
The scalability, reliability, and ease of integration provided by REST APIs facilitate seamless interactions between clients and servers, thereby enhancing the performance and flexibility of complex software ecosystems. 
Their widespread adoption underscores their importance in today's technology landscape, where rapid communication and data accessibility are paramount.

\subsection{Challenges of Fault Localization in REST APIs}
While REST APIs have simplified the development and management of modern applications, they introduce specific challenges that complicate fault localization.
The architecture often involves non-code artifacts such as API specifications, configuration files, and database schemas, which are not traditionally addresses by fault localization techniques developed for code-centric applications.

\subsection{Gaps in Current Research}
Fault localization is a well-established research area within software engineering, focusing primarily on identifying the locations of faults in conventional software systems to reduce debugging time and enhance system reliability.
 However, the unique operational dynamics and architectural complexities of REST APIs pose new challenges that are not fully addressed by existing fault localization techniques.
Previous studies have developed fault taxonomies for REST APIs which are helpful if the FL techniques can localize faults to understand what categories of faults can be localized.
There remains a significant knowledge gap regarding the effectiveness of these techniques in accurately identifying and localizing faults in REST APIs, particularly those involving non-code artifacts.

\subsection{Need for Targeted Research on Fault Localization in REST APIs}
This research is motivated by the critical need to evaluate and understand the performance of existing fault localization techniques within the REST API context. 
By determining how effectively these techniques can identify and localize faults in REST APIs, developers can gain valuable insights that could lead to quicker and more accurate fault diagnosis. This is particularly important as even minor faults can escalate into major disruptions in REST API-dependent systems, affecting user experience and operational efficiency. Addressing this gap will not only contribute to the field by enhancing the robustness and reliability of REST APIs but also by supporting the development of more sophisticated tools and methodologies tailored to the needs of modern software architectures.

\subsection{Research Objectives}
The primary objective of this research is to systematically assess the applicability of established fault localization techniques—namely 
BLUES and LLMAO to a curated dataset of REST API faults. 
This dataset will be developed to encompass a broad spectrum of typical faults in REST APIs and will be classified according to an existing comprehensive taxonomy. 
The insights gained from this study are expected to reveal whether traditional fault localization methods are suitable for the complex environments of REST APIs and may guide future efforts in refining these techniques or developing new approaches specifically designed for REST API ecosystems.

\begin{figure*}[t] 
    \centering
    \includegraphics[width=1.0\textwidth]{fig2.png}
    \caption{Approach Overview}
    \label{fig:widefigure}
  \end{figure*}

\section{Related Work}
\label{sec:relatedwork}

Fault localization techniques have long been an integral part of software maintenance, aiding developers by pinpointing the origins of failures within software systems. 
A variety of approaches have been explored ~\cite{Wong2023_Software_Fault_localization}, including Information Retrieval (IR) based methods, Spectrum-Based Fault Localization (SFL), and more comprehensive software engineering tools.

Information Retrieval Based Fault Localization: The work by Klaus Changsun Youm et al introduces an advanced IR-based fault localization method called BLIA, which integrates bug reports and code change history to enhance the localization process  ~\cite{7467300} ~\cite{ctx114059874780001451}. BLIA notably improves the accuracy of locating bugs by analyzing texts, stack traces, and comments within bug reports alongside source file structures and version histories. This method has shown significant improvements over previous tools such as BugLocator and BLUiR, particularly at the file and method levels, by refining the granularity of localization results. This approach underscores the potential of IR-based methods in handling complex software systems, aligning with the need to explore such techniques within REST API environments.

The Jaguar tool, described by Ribeiro et al, utilizes SBFL technique to identify faulty code excerpts in Java programs ~\cite{8367068}. By employing both control-flow and data-flow spectra and integrating the lightweight ba-dua coverage tool, Jaguar efficiently supports the analysis of large programs. The capability of Jaguar to provide detailed visualizations of suspicious program elements highlights the effectiveness of SFL in traditional software environments. The distinction between data-flow and control-flow spectra offers a nuanced view of fault localization that could be pertinent to analyzing REST APIs, known for their complex interactions and stateless operations.

Debugging in IDEs, particularly using tools like Visual Studio Code for web applications, illustrates the practical aspects of fault localization in real-world scenarios ~\cite{DebuggingCode}. The capabilities of IDEs to facilitate debugging through breakpoints and variable inspections are directly relevant to the challenges faced in REST API development, where faults may not only arise from code but also from API configurations and interactions.

\section{Approach}
\label{sec:approach}

@@

To effectively assess the applicability of fault localization techniques to REST APIs, In our research, we utilize a set of REST API services previously employed in the study "Generating REST API Specifications through Static Analysis" by Manish et al ~\cite{ManishRestServices}. These services are chosen due to their diverse characteristics and well-documented configurations, making them suitable subjects for evaluating fault localization techniques. 
The faults from these services will be categorized based on a previously established taxonomy of REST API faults, ensuring that each fault type is adequately represented. We are three graduate students with knowledge on REST API, we have selected the issues on GitHub Repositories, and we have the read the messages of their issues and saw what were the changes made and given it a fault type. We all have gone through all the services and then we together consolidated into one single list where we found 26 Faults which we can test using the Fault Localization Techniques.

\subsection{Selection of Fault Localization Techniques}

The study will focus on two primary fault localization techniques that have shown promise in traditional software contexts but whose effectiveness in REST APIs remains underexplored:
\begin{enumerate}
    \item \textbf{BLUES:} ~\cite{ManishBluesFaultLocalization} BLUES is developed by a group of researchers Manish et al which takes Bug report as input and generates the suspicious ranked list of faulty code.
    \item \textbf{LLMAO:} ~\cite{LLMAOFaultLocalization} LLMAO is developed by a group of researchers Aidan et al, where LLMAO is first LLM (Large Language Model) based for fault localization and which takes no inputs. But it finds the difference between two commits to see where the bug was introduced and creates a ranked list of faulty code.

\end{enumerate}

Both the Fault Localization Techniques are known for their effective finding of the faulty code. And also both the techniques are new.

\subsection{Integration with REST API Characteristics}

Given the unique challenges posed by REST APIs, such as stateless operations and the presence of non-code artifacts (e.g., configuration files and API specifications), our approach will also consider these elements:
\begin{itemize}
    \item \textbf{Non-Code Artifacts}: Special attention will be given to faults that may originate from or affect non-code artifacts. 
\end{itemize}

\begin{figure*}[t]
    \caption{Issue Types}
    \label{fig:issueTypes}
    \begin{tabular}{|m{3cm}|m{3 cm}|m{5cm}|m{5cm}|}
    \hline
    \textbf{Concurrency Issues} & \textbf{Configuration Issues} & \textbf{Implementation Issues} & \textbf{Verification and Validation Issues} \\
    \hline
    Concurrency Issue & Environment Incompatibility & \textbf{Coding Issues:} & Request Verification \\
     &  & Hardcoded &  \\
     & Incorrect Configuration & Off by one Error & Unexpected Error Code \\
     &  & Unsupported Code &  \\
    \hline
     &  & \textbf{Processing Issues:} &  \\
     &  & Incorrect Input Processing &  \\
     &  & Incorrect Memory Handling &  \\
     &  & Redundant Value &  \\
    \hline
     &  & \textbf{Indexing Issues:} &  \\
     &  & Unique Index or Primary Key &  \\
    \hline
    \end{tabular}
\end{figure*}

\section{Evaluation}
\label{sec:evaluation}

\subsection{Dataset}
\label{sec:dataset}

@@

The fault taxonomy utilized in our study delineates four major fault types, each encompassing various sub-categories as outlined in ~\cite{automatedTestTaxonomy}. Collectively, these categories provide a comprehensive framework, dividing the faults into a total of 19 distinct categories. 
This detailed classification aids in systematically analyzing and categorizing the faults encountered during the testing of REST APIs to create the Table ~\ref{tab:faultData}

\begin{table}[ht]
    \centering
    \caption{Fault Data}
    \label{tab:faultData}
    \begin{tabular}{|c|c|c|}
    \hline
        \hline
        \textbf{No.} & \textbf{Fault Type} & \textbf{\# of Faults} \\ \hline
        1 & Concurrency Issue & 2 \\ \hline
        2 & Environment Incompatibility &  1 \\ \hline
        3 & Hardcoded & 1 \\ \hline
        4 & Incorrect Configuration & 3 \\ \hline
        5 & Incorrect Input Processing & 4 \\ \hline
        6 & Incorrect Memory Handling & 1 \\ \hline
        7 & Off by one error & 1 \\ \hline
        8 & Redundant Value & 1 \\ \hline 
        9 & Regression Failure & 1 \\ \hline 
        10 & Request Verification & 2 \\ \hline
        11 & Unexpected Error Code & 1 \\ \hline
        12 & Unique Index or Primary Key & 2 \\ \hline
        13 & Unsupported Input & 4 \\ \hline
    \end{tabular}
\end{table}

\subsection{Metrics}
\label{sec:metrics}

There are several metrics that can be used to evaluate how effective FL techniques are at localizing REST API faults. In this research, two primary metrics to consider are \textbf{Top-k Accuracy}, and \textbf{EXAM}.

\textbf{Top-k Accuracy:} This metric measures the percentage of actual faulty statements found within the top k position of the ranking generated by an FL technique. The ranking positions are based on how likely each statement is considered faulty according to the fault localization algorithm. This metric is useful for evaluating how effective FL techniques are at localizing faults. In this research, several values of k are used to measure the FL technique's performance, such as top-1, top-5, and top-10.
\\
This metric measures the percentage of times the actual faulty statements are within the top $k$ positions of a ranked list produced by the fault localization technique. Mathematically, it is expressed as:
    \[
        \text{Top-k} = \frac{\text{ \#faults found in top } k \text{ positions}}{\text{Top k positions}} \times 100\%
    \]

    This metric evaluates the effectiveness of fault localization techniques by their ability to rank the actual faulty statements highly on the list.
    \\

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{tabularx}
\usepackage{tcolorbox}
\usepackage{array}
\usepackage{fancybox}

@@

% \title{Do Automated Fault Localization Techniques Work For REST APIs?}
\title{Developing a Comprehensive Taxonomy for REST API Faults: Insights from Real-World Bug Reports}

@@

\begin{abstract}
    The increasing reliance on REST APIs in modern web applications has highlighted the need for effective fault localization techniques. 
    Existing taxonomies for REST API faults, primarily based on automated test generation tools, focus on error messages and status codes. 
    However, these taxonomies often fail to account for real world issues that can occur in REST APIs, leading to a gap in fault classification. 
    In this study, we analyze real-world bug reports from GitHub to develop a comprehensive taxonomy that encompasses a wider range of fault types. 
    By examining 24 bug reports, we identified 12 distinct categories of faults that are not adequately represented in current taxonomies. 
    Our findings indicate that combining test suite-based taxonomies with bug report-based taxonomies can bridge the gap, providing a more holistic understanding of faults in REST APIs. 
    This new taxonomy aims to enhance fault localization, improve API robustness, and better align with real-world scenarios encountered by developers.
    Alongside this taxonomy, we created a benchmark for evaluating these 24 bugs, which are real world bugs. \\
\end{abstract}

\begin{IEEEkeywords}
Fault Localization, REST APIs, Taxonomies
\end{IEEEkeywords}

% ------------------- Introduction -------------------
\section{Introduction}
\label{sec:introduction}

REST APIs (Representational State Transfer) have become backbone of the modern web and cloud applications. 
They facilitate seamless interactions between client and server through stateless communication, enabling services to be scalable, reliable, and easily integrateable ~\cite{li2016} ~\cite{neumann2018}. 
Basically, REST APIs are a set of rules and standards  defined by OpenAPI ~\cite{ed-douibi2018} used to enable communication between different software applications over the internet. They are built around the use of standard HTTP methods such as GET, POST, PUT, and DELETE to interact with resources, which are any kind of data or service that can be named on a network.
Given their critical role, the effective identification and resolution of faults within REST APIs remain a significant challenge ~\cite{barbir2007}, prompting the need for research on how well the existing taxonomy align with real-world scenarios.

As systems that rely on REST APIs grow in scale and complexity  ~\cite{khare2004} , minor faults can escalate into major disruptions, impacting user experience and business operations. 
So it is important to understand the real-world faults, but there are many faults that can be existing in the context of REST APIs. And we need a detailed taxonomy to cluster these real-world bugs into meaningful categories. So, that we can prioritize and diagnose the critical faults in REST APIs.

Our initial assumption was that the existing taxonomy, developed from automated test generation tools, would align well with real-world bug reports from GitHub. 
To empirically test this assumption, we conducted a study analyzing a set of bug reports from various REST API projects on GitHub. 
Our findings revealed that the existing taxonomy failed to account for real world issues that can occur under successful response codes (e.g., 200 OK). Also, the paper "On the Faults Found in REST APIs by Automated Test Geneation" ~\cite{automatedTestTaxonomy} was limited to the test suite based results and they made a taxonomy based on those results. 
This significant misalignment between the test suite based taxonomy and with real world bugs highlighted the need for a new, comprehensive taxonomy.

Given the shortcomings of the existing taxonomy, our primary objective was to develop a new taxonomy that better represents the faults encountered in real-world scenarios. 
Alongside this taxonomy, we aimed to create a benchmark for evaluating these faults, providing a structured framework for assessing and improving REST API reliability.

And the combining the test-suite based taxonomy and the bug report-based taxonomy, we created a comprehensive taxonomy that encompasses a wider range of faults. 
This new taxonomy aims to provide a more holistic understanding of faults in REST APIs, improving API robustness, and better align with real-world scenarios.

Our Assumptions:

\begin{itemize}
    \item 	\textit{Assumption 1}: We assume that the findings and the new taxonomy can be generalized to other REST API projects beyond the ones specifically analyzed in this study.
    \item   \textit{Assumption 2}: 	We assume that the new taxonomy will provide better diagnostic capability for developers, allowing them to identify, categorize, and prioritize faults more effectively.
\end{itemize}

The motivation for this research stems from the critical need to address the gap between theoretical fault models derived from automated test generation tools and the practical issues encountered in real-world REST API applications. 
Existing taxonomies primarily focus on certain types of errors, such as 500-based errors, and often fail to account for faults that occur under successful response codes like 200 OK. 
This misalignment limits the ability of developers to effectively diagnose, categorize, and prioritize faults. By creating a new, comprehensive taxonomy based on real-world bug reports, we aim to provide a more accurate and practical framework for understanding REST API faults. 
This taxonomy will enhance  fault understanding process, improve system reliability, and better support developers in maintaining robust and resilient REST API-based systems.

To guide our investigation and address the identified gaps, we formulated the following research questions:
\begin{enumerate}
    \item \textbf{RQ1:} What categories of faults are most prevalent in real-world REST API bug reports?
    \item 
\end{enumerate}

For the evaluation dataset, we will manually select the issues from the GitHub services and their fixes from REST API projects that utilize Spring Boot or Jersey frameworks. These GitHub services are used in the paper  \textit{Generating REST API Specifications through Static Analysis} by Manish et al ~\cite{ManishRestServices}
This dataset will encompass various categories of faults identified in REST APIs. By analyzing repositories and commit histories, we will extract specific instances where bugs have been documented and subsequently fixed.

Our analysis of bug reports led us to create a benchmark of 24 bugs which were classified with a taxonomy based on bug reports.

In the following sections we will describe our methodology and results.

% This research is motivated by the need to evaluate how well current fault localization techniques perform in the unique context of REST APIs. 
% The goal is to determine if these techniques can indeed be applied effectively to REST APIs and, if so, to explore which types of faults are more amenable to being localized. 
% This understanding could potentially allow developers to more efficiently diagnose and address issues, thereby enhancing the stability and performance of REST API-based systems.

% Fault localization is a well-established area of research within software engineering, traditionally concentrated on more conventional software systems. 
% REST APIs, however, present distinct challenges that complicate fault localization due to their composition and operational dynamics. 
% Additionally, the architecture of REST APIs often involves diverse artifacts that are not source code, such as configuration files, API specifications, and database schemas.

% The primary objective of this research is to evaluate the effectiveness of existing fault localization techniques within the unique context of REST APIs, which feature a mix of code and non-code artifacts. 
% This study will systematically apply established fault localization methods like BLUES ~\cite{ManishBluesFaultLocalization} and LLMAO ~\cite{LLMAOFaultLocalization} to a dataset of REST API faults. 
% This dataset will be meticulously developed to represent a wide range of faults typical in REST APIs and classified according to an existing comprehensive taxonomy derived from previous research.

% This approach will enable us to assess the applicability of these fault localization techniques to REST APIs by determining how effectively they can identify and localize different types of faults. 
% The analysis will provide insights into whether traditional fault localization methods are suited to the complexities of REST APIs, especially considering their unique structural and functional characteristics.

% % ----------------- Assumptions -----------------
% Our assumptions:
% \begin{itemize}
%     \item \textit{Assumption 1:} Assume that the dataset of REST API faults would fit in the taxonomy that we have developed. 
%     \item \textit{Assumption 2:} Assume that the selected fault localization techniques are suitable for application to REST APIs, despite their original design for conventional software systems. This includes the assumption that these techniques can handle the unique challenges posed by REST APIs, such as dealing with non-code artifacts.
% \end{itemize}

% % ------------------- Research Questions -------------------
% The primary research questions are formulated as follows:
% \begin{itemize}
%     \item \textbf{RQ1:} What categories of faults are most effectively localized by current techniques?
%     \item \textbf{RQ2:} Which fault localization technique is highly effective in the context of REST APIs?
% \end{itemize}

% For the evaluation dataset, we will manually select the issues from the GitHub services and their fixes from REST API projects that utilize Spring Boot or Jersey frameworks. These GitHub services are used in the paper  \textit{Generating REST API Specifications through Static Analysis} by Manish et al ~\cite{ManishRestServices}
% This dataset will encompass various categories of faults identified in REST APIs. By analyzing repositories and commit histories, we will extract specific instances where bugs have been documented and subsequently fixed. 
% The categorization of these faults will be categorized with an established taxonomy of API faults ~\cite{automatedTestTaxonomy} , ensuring that each bug is classified according to its nature and impact. This rigorous dataset compilation aims to provide a comprehensive basis for testing fault localization techniques within a controlled, relevant environment.

% For evaluation of fault localization techniques using the dataset derived from REST APIs employing Spring Boot and Jersey frameworks will be measured by Top-k accuracy, and EXAM score.
% These metrics will collectively provide a thorough assessment of each fault localization technique's ability to detect and accurately categorize faults in REST APIs, contributing to a detailed understanding of their practical utility and areas for improvement.

% ------------------- Background and Motivation -------------------
\section{Background and Motivation}
\label{sec:background-and-motivation}

\subsection{Importance of REST APIs}
REST APIs (Representational State Transfer APIs) are central to modern web and cloud applications, serving as critical conduits for data exchange and system integration. 
They leverage standard HTTP methods like GET, POST, PUT, and DELETE to interact with networked resources, making them integral to the architecture of distributed systems. 
The scalability, reliability, and ease of integration provided by REST APIs facilitate seamless interactions between clients and servers, thereby enhancing the performance and flexibility of complex software ecosystems. 
Their widespread adoption underscores their importance in today's technology landscape, where rapid communication and data accessibility are paramount.

% \subsection{Challenges of Fault Localization in REST APIs}
% While REST APIs have simplified the development and management of modern applications, they introduce specific challenges that complicate fault localization.
% The architecture often involves non-code artifacts such as API specifications, configuration files, and database schemas, which are not traditionally addresses by fault localization techniques developed for code-centric applications.

\subsection{Gaps in Current Research}
% Fault localization is a well-established research area within software engineering, focusing primarily on identifying the locations of faults in conventional software systems to reduce debugging time and enhance system reliability.
%  However, 
The unique operational dynamics and architectural complexities of REST APIs pose new challenges that are not fully addressed by existing to create a comprehensive taxonomy.
Previous studies have developed fault taxonomies for REST APIs which are helpful only in categorizing based on the failed test cases.
% if the FL techniques can localize faults to understand what categories of faults can be localized.

% \subsection{Need for Targeted Research on Fault Localization in REST APIs}
% This research is motivated by the critical need to evaluate and understand the performance of existing fault localization techniques within the REST API context. 
% By determining how effectively these techniques can identify and localize faults in REST APIs, developers can gain valuable insights that could lead to quicker and more accurate fault diagnosis. This is particularly important as even minor faults can escalate into major disruptions in REST API-dependent systems, affecting user experience and operational efficiency. Addressing this gap will not only contribute to the field by enhancing the robustness and reliability of REST APIs but also by supporting the development of more sophisticated tools and methodologies tailored to the needs of modern software architectures.

% \subsection{Research Objectives}
% The primary objective of this research is to systematically assess the applicability of established fault localization techniques—namely 
% BLUES and LLMAO to a curated dataset of REST API faults. 
% This dataset will be developed to encompass a broad spectrum of typical faults in REST APIs and will be classified according to an existing comprehensive taxonomy. 
% The insights gained from this study are expected to reveal whether traditional fault localization methods are suitable for the complex environments of REST APIs and may guide future efforts in refining these techniques or developing new approaches specifically designed for REST API ecosystems.

\begin{figure*}[t] 
    \centering
    \includegraphics[width=1.0\textwidth]{FaultTaxonomyFlow.png}
    \caption{Approach Overview}
    \label{fig:widefigure}
  \end{figure*}

%   ------------- Related Work -------------
\section{Related Work}
\label{sec:relatedwork}

\begin{figure*}[t] 
    \centering
    \includegraphics[width=0.8\textwidth]{TaxonomyDeveloped.png}
    \caption{Developed Taxonomy}
    \label{fig:TaxonomyDeveloped}
  \end{figure*}

% Fault localization techniques have long been an integral part of software maintenance, aiding developers by pinpointing the origins of failures within software systems. 
% A variety of approaches have been explored ~\cite{Wong2023_Software_Fault_localization}, including Information Retrieval (IR) based methods, Spectrum-Based Fault Localization (SFL), and more comprehensive software engineering tools.

% BLUES (Bug Localization Using Error Messages and Stack Traces) is a fault localization technique designed to enhance the accuracy and efficiency of identifying the sources of bugs in software systems. Developed by  Manish et al ~\cite{ManishBluesFaultLocalization} , BLUES leverages bug reports to pinpoint potential fault locations within the codebase.

% LLMAO is a fault localization technique that leverages large language models (LLMs) to identify and rank potential fault locations within software systems. Developed to utilize the capabilities of advanced LLMs, LLMAO provides a novel approach to fault localization by analyzing code changes and utilizing commit history.

% And there is a
% The paper about the fault taxonomy, The paper titled “On the Faults Found in REST APIs by Automated Test Generation” \cite{automatedTestTaxonomy} investigates the types of faults that can be uncovered through the use of automated test generation tools. This research provides a taxonomy of faults specifically found in REST APIs by analyzing the failures encountered during automated testing.
% This is the only paper we found which was trying to create a taxonomy of faults for the REST API applications, as it was limited to the test suite based results and they made a taxonomy based on those results. Also, the classification they have done heavily manual and there is not automated classification method that exists right now which can address the issue of clustering the faults into categories

The paper titled “On the Faults Found in REST APIs by Automated Test Generation” \cite{automatedTestTaxonomy} investigates the types of faults that can be uncovered through the use of automated test generation tools. This research provides a taxonomy of faults specifically found in REST APIs by analyzing the failures encountered during automated testing. The study meticulously categorizes various fault types based on the error messages and behavior observed when automated test cases are executed against REST API endpoints.

This is the only paper we found that attempts to create a comprehensive taxonomy of faults for REST API applications. However, its scope is limited to faults identified through test suites. The taxonomy developed in this research is based on the results of these automated tests, which primarily detect faults resulting in error status codes, such as 500 Internal Server Errors. Consequently, this taxonomy may not capture the full range of faults that occur in real-world scenarios, particularly those that manifest under successful response codes.

Furthermore, the classification process in this paper is heavily manual, involving significant human effort to categorize the faults based on their characteristics. Currently, there is no automated classification method that can effectively cluster these faults into meaningful categories. This reliance on manual classification poses challenges in scalability and consistency, as the subjective nature of human judgment can lead to variations in fault categorization.

Overall, while this research provides valuable insights and a foundational taxonomy for REST API faults, its limitations highlight the need for a more comprehensive and automated approach to fault classification. 
% Our research aims to address these gaps by developing a new taxonomy based on real-world bug reports and creating a benchmark for evaluating faults, which will facilitate more accurate and efficient fault localization in REST API systems.

% Debugging in IDEs, particularly using tools like Visual Studio Code for web applications, illustrates the practical aspects of fault localization in real-world scenarios ~\cite{DebuggingCode}. The capabilities of IDEs to facilitate debugging through breakpoints and variable inspections are directly relevant to the challenges faced in REST API development, where faults may not only arise from code but also from API configurations and interactions.

%   ------------- Approach ------------
\section{Approach}
\label{sec:approach}

@@

% To effectively assess the applicability of fault localization techniques to REST APIs.
In our research, we utilize a set of REST API services previously employed in the study "Generating REST API Specifications through Static Analysis" by Manish et al ~\cite{ManishRestServices}. These services are chosen due to their diverse characteristics and well-documented configurations, making them suitable subjects for evaluating fault localization techniques. 
% The faults from these services will be categorized based on a previously established taxonomy of REST API faults, ensuring that each fault type is adequately represented.

We are three graduate students with knowledge on REST API, we have selected the issues on GitHub Repositories, and we have the read the bug reports of the issues and saw what were the changes made and assigned it a fault type. We all have gone through all the services and then we together consolidated into one single list where we found 24 Faults which we can test using the Fault Localization Techniques. 
There were almost 50 bugs we had discussed, and we are confident about these 24 bugs in our dataset. And the others are pruned for now because we are not confident enough about those.

% \subsection{Selection of Fault Localization Techniques}

% The study will focus on two primary fault localization techniques that have shown promise in traditional software contexts but whose effectiveness in REST APIs remains underexplored:
% \begin{enumerate}
%     \item \textbf{BLUES:} ~\cite{ManishBluesFaultLocalization} BLUES is developed by a group of researchers Manish et al which takes Bug report as input and generates the suspicious ranked list of faulty code.
%     \item \textbf{LLMAO:} ~\cite{LLMAOFaultLocalization} LLMAO is developed by a group of researchers Aidan et al, where LLMAO is first LLM (Large Language Model) based for fault localization and which takes no inputs. But it finds the difference between two commits to see where the bug was introduced and creates a ranked list of faulty code. 
% \end{enumerate}

% Both the Fault Localization Techniques are known for their effective finding of the faulty code. And also both the techniques are new.

\subsection{Integration with REST API Characteristics}
Given the unique challenges posed by REST APIs, such as stateless operations and the presence of non-code artifacts (e.g., configuration files and API specifications), our approach will also consider these elements:
\begin{itemize}
    \item \textbf{Non-Code Artifacts}: Special attention will be given to faults that may originate from or affect non-code artifacts. 
\end{itemize}

% \begin{figure*}[t]
%     \caption{Issue Types}
%     \label{fig:issueTypes}
%     \begin{tabular}{|m{3cm}|m{3 cm}|m{5cm}|m{5cm}|}
%     \hline
%     \textbf{Concurrency Issues} & \textbf{Configuration Issues} & \textbf{Implementation Issues} & \textbf{Verification and Validation Issues} \\
%     \hline
%     Concurrency Issue & Environment Incompatibility & \textbf{Coding Issues:} & Request Verification \\
%      &  & Hardcoded &  \\
%      & Incorrect Configuration & Off by one Error & Unexpected Error Code \\
%      &  & Unsupported Code &  \\
%     \hline
%      &  & \textbf{Processing Issues:} &  \\
%      &  & Incorrect Input Processing &  \\
%      &  & Incorrect Memory Handling &  \\
%      &  & Redundant Value &  \\
%     \hline
%      &  & \textbf{Indexing Issues:} &  \\
%      &  & Unique Index or Primary Key &  \\
%     \hline
%     \end{tabular}
% \end{figure*}

%   ------------- Evaluation ------------
\section{Evaluation}
\label{sec:evaluation}

%   ------------- Dataset ------------
\subsection{Dataset}
\label{sec:dataset}

@@

Our initial assumption that the existing taxonomy would be sufficient proved incorrect, prompting us to develop our own taxonomy. 
When we encountered issues not covered by the existing taxonomy, we created new categories. Out of the 24 bugs analyzed, only 2 could be classified using the existing taxonomy. 
However, even for these, the alignment between the bug reports and the fault type definitions was not ideal.

\subsection{The Taxonomy}
\label{sec:newtaxonomy}

Based on our analysis of the 24 bug reports from various REST API projects, we developed a comprehensive taxonomy ~\ref{fig:TaxonomyDeveloped} that encompasses a broader range of fault types not adequately captured by existing taxonomies. This new taxonomy is categorized into major fault categories, each containing specific fault types.

Major Categories and Fault Types

\subsection{Major Categories and Fault Types}

\begin{enumerate}
    \item \textbf{Concurrency Issues}
    \begin{itemize}
        \item \textbf{Concurrency Issue:} This fault refers to a scenario known as a race condition in concurrent programming, where two functions are intended to execute sequentially but run simultaneously instead. This can result in one function depending on the output of the other function before it has completed, leading to erroneous outcomes or failures.
    \end{itemize}

    \item \textbf{Configuration Issues}
    \begin{itemize}
        \item \textbf{Environment Incompatibility:} These are the kind of errors which arise due to the environments such as Operating System, Hardware Environment, or Network Environment, where the code written for one environment doesn't translate to another environment.
        \item \textbf{Incorrect Configuration:} This fault refers to errors or mistakes in the setup or configuration of a system, software, or application. Misconfiguration can lead to unexpected behavior, errors, or issues.
    \end{itemize}

    \item \textbf{Implementation Issues}
    \begin{itemize}
        \item \textbf{Coding Issues:}
        \begin{itemize}
            \item \textbf{Hard-coded:} This fault type occurs when a value is invalid due to being Hard-Coded within the software.
            \item \textbf{Off by one Error:} An off-by-one error refers to a programming mistake where the application incorrectly processes or manipulates data, resulting in either accessing one more or one less element than intended, leading to unintended behavior or functional errors in the web application.
            \item \textbf{Unsupported Input:} This issue occurs when the documented functionality or parameters are not implemented or supported in the actual codebase or system. This discrepancy can lead to unexpected behaviors, errors, or limitations when utilizing the software based on the documented specifications.
        \end{itemize}

        \item \textbf{Processing Issues:}
        \begin{itemize}
            \item \textbf{Incorrect Input Processing:} Incorrect input processing in web applications refers to the improper handling of user inputs, leading to issues such as errors in API responses, unexpected behavior, and inconsistencies in the way data is processed and displayed. This can result in inaccuracies, unexpected outcomes, and functionality failures within the web application.
            \item \textbf{Incorrect Memory Handling:} Incorrect memory handling involves inadequate or absent measures to limit or manage memory usage within a system, potentially leading to issues like memory exhaustion, performance degradation, or system instability.
            \item \textbf{Redundant Value:} This fault type refers to an unnecessary or duplicated data point or condition within a system, schema, or dataset. It indicates an extra check or condition that adds complexity without providing any additional benefit in terms of data validation or processing logic.
        \end{itemize}
